\input slix

\def\prop{{\bf Proposal: }}
\def\opts{{\bf Options:}\numberList}
\let\endOpts=\endNumberList
\def\dstore#1{$\langle\hbox{#1}\rangle$}

\title{YANG Types for DNS Classes and Resource Record Types}
\subtitle{\normalSize\tt draft-lhotka-dnsop-iana-class-type-yang-01}

\author{Ladislav Lhotka}{lhotka@nic.cz}
\authorB{Petr Špaček}{petr.spacek@nic.cz}

\date [2019-03-26]

\slide[Summary]

Two IANA registries from [1] are defined as YANG derived types:

\bulletList

\item DNS CLASSes
\item Resource Record (RR) Types

\endBulletList

\medskip

{\bf Changes since -00}

\bulletList

\item Only in the I-D text: more details about the context and use cases.

\item The YANG module is exactly the same as in -00.

\endBulletList

\medskip
{\bf Issues raised}

\numberList

\item Can the YANG module and registry ever get out of sync?

\item Semantics of {\it deprecated}.

\endNumberList

\vfill
{\petit
[1]~\URL{https://www.iana.org/assignments/dns-parameters/dns-parameters.xhtml}}

\slide[YANG Derived Types]

One type is an enumeration of mnemonic names, the other also permits a
numeric reference (cf. RFC 3597).

{\petit

\twoColumn{0.45}{0.45}

\verbatim
typedef «dns-class-name» {
  type enumeration {
    enum IN {
      value "1";
      ...
    }
    enum CH {
      value "3";
      ...
    }
    ...
  }
}

typedef «dns-class» {
  type union {
    type uint16;
    type dns-class-name;
  }
  ...
}
§

\rightColumn
 
\verbatim
typedef «rr-type-name» {
  type enumeration {
    enum A {
      value "1";
      ...
    }
    enum NS {
      value "2";
    ...
    }
    ...
  }
}

typedef «rr-type» {
  type union {
    type uint16;
    type rr-type-name;
  }
  ...
}
§}

\endColumn

\slide[Issue \#1: YANG module versus registry]

If there is a flaw in the registry, can it be fixed in the YANG module
independently of the registry?

We recommend not to do so: it could break the assumption that further
updates to the module will be done by IANA based of the registry
changes.

\slide[Issue \#2: semantics of {\it deprecated}]

\bulletList

\item RFC 8126 (IANA registries):

{\it Specific entries in a registry can be marked as "obsolete" (no longer
in use) or "deprecated" (use is not recommended).}

\item RFC 7950 (YANG):

{\it “deprecated” indicates an obsolete definition, but it permits
new/continued implementation in order to foster interoperability with
older/existing implementations.}

\endBulletList

This issue is currently being discussed in the NETMOD WG, and should
be resolved in the next version of YANG.

\bye
